Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-10-07 paper/lncsFormat.tex
finish sec 2.1.1.3; 5274 words (related works)(event detection).(without extra information).(topic model)

Most existing methods are implemented \textit{without extra information}.
They utilize the bursty pattern in the text stream to detect events, and are carried out by  clustering articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, analyzing word frequencies\cite{Mathioudakis:2010fc,Weng:2011wz}, or finding bursty topics\cite{Diao:2012wj,Yan:2015wm}. 
(1) By clustering articles, UMass\cite{Allan:2000wu}, LSH\cite{Petrovic:2010uj}, k-Term-FSD\cite{Wurzer:2015wq} and other similar methods model the occurred events as clusters of articles, and link the incoming article with an already existed event cluster or label it as the first story of a new event.
The decision is based on whether the dissimilarity between the incoming article and existed event clusters is over the user-specified threshold. 
Taking LSH as an example, as \cite{Petrovic:2010uj} discussed, the threshold controls the result: the big one leads to very few and broad clusters, while the small one results in very small and specific clusters.
Even after carefully set the appropriate threshold, the clusters generated by this kind method are still mixed of events and non-events due to large portion of non-event microblogs, which requires some post-processing methods as the supplement. 
(2) By analyzing word frequencies, TwitterMonitor\cite{Mathioudakis:2010fc} models the bursty words by queueing theory, and EDCoW\cite{Weng:2011wz} exploits wavelet transformation, which converts signal from time domain to time-scale domain, to detect the change point of word signal. 
However they treat the word as the most basic unit in analysis, without regarding how many concepts are represented by the word.
(3) By finding bursty topics, TimeUserLDA, BurstyBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.

%The unsupervised methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.

The reason why this kind methods cannot achieve high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
This kind methods ``understand" the document only by the recent data and the frequencies of the data, but the ``understanding" is not so confident that they still need the specific threshold to help to make decision. In the journalist metaphor of news value theory, they have the limited knowledge of normal states (aka "routine things") due to the limited history information used. 
On the one hand, UMass\cite{Allan:2000wu} prefers the lower threshold to enlarge the recall but suffers the precision.

@@

%TODO LSH-FSD\cite{Petrovic:2010uj}没有评测FSD的情况，我们也可以提一句，我们不评测FSD，我们只评测检测出的事件是否是真实的事件。
\begin{table}[h]
\scriptsize
\centering
\scalebox{0.95}{
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
    UMass System & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
    LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
    TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
    Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
    EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
    BurstyBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
    \textsc{LTDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
    \end{tabular}
}
\caption{Overall Performance on Event Detection}
\end{table}

>>>>

Most existing methods are implemented \textit{without extra information}.
They utilize the bursty pattern in the text stream to detect events, and are carried out by  clustering articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, analyzing word frequencies\cite{Mathioudakis:2010fc,Weng:2011wz}, or finding bursty topics\cite{Diao:2012wj,Yan:2015wm}. 
(1) By clustering articles, UMass\cite{Allan:2000wu}, LSH\cite{Petrovic:2010uj}, k-Term-FSD\cite{Wurzer:2015wq} and other similar methods model the occurred events as clusters of articles, and link the incoming article with an already existed event cluster or label it as the first story of a new event.
The decision is based on whether the dissimilarity between the incoming article and existed event clusters is over the user-specified threshold. 
Taking LSH as an example, as \cite{Petrovic:2010uj} discussed, the threshold controls the result: the big one leads to very few and broad clusters, while the small one results in very small and specific clusters.
Even after carefully set the appropriate threshold, the clusters generated by this kind method are still mixed of events and non-events due to large portion of non-event microblogs, which requires some post-processing methods as the supplement. 
(2) By analyzing word frequencies, TwitterMonitor\cite{Mathioudakis:2010fc} models the bursty words by queueing theory, and EDCoW\cite{Weng:2011wz} exploits wavelet transformation, which converts signal from time domain to time-scale domain, to detect the change point of word signal. 
However they treat the word as the most basic unit in analysis, without regarding how many concepts are represented by the word.
(3) By finding bursty topics via topic modelling, TimeUserLDA\cite{Diao:2012wj}, BurstyBTM\cite{Yan:2015wm} generates detected events.
TimeUserLDA distinguishes user's long term interests and short term bursty events, and BurstyBTM utilizes the burstiness of biterms as prior knowledge.
They both need to set the appropriate number of topics to run the topic modelling, and detect the ``large" events that associate with many articles but ignore the ``small" ones. 
To summarize, due to microblog's short length and high noise, it's not easy to set the directly applicable parameter for existing methods to achieve high precision and high recall simultaneously.

The second group methods detect events by \textit{leveraging extra information}. 
\cite{huang2016efficient} incorporates user's and the followees' profiles in microblog platform as the extra information for modeling user's long term interests, and further detects the bursty events which draws the attention of users with different interests. 
However many event detection scenes only provide the microblog stream without user profile information and the following network. 
FrameNet?.
Wikipop\cite{ciglan2010wikipop}.
\cite{mcminn2013building} leverages LSH, wikipedia to build a large corpus for evaluating event detection on twitter.
\cite{osborne2012bieber} utilizes Wikipedia for filtering spurious events.
\cite{steiner2013mj} utilizes the concurrent wikipedia edit spikes for event detection.
%The unsupervised methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.

%The reason why this kind methods cannot achieve high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
%This kind methods ``understand" the document only by the recent data and the frequencies of the data, but the ``understanding" is not so confident that they still need the specific threshold to help to make decision.

@@

%TODO LSH-FSD\cite{Petrovic:2010uj}没有评测FSD的情况，我们也可以提一句，我们不评测FSD，我们只评测检测出的事件是否是真实的事件。
\begin{table}[h]
\scriptsize
\centering
\scalebox{0.95}{
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
    LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
    TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
    Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
    EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
    BurstyBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
    \textsc{LTDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
    \end{tabular}
}
\caption{Overall Performance on Event Detection}
\end{table}
